class: split-30

.row.split-two[
.row[.content[
# Edit the text and code section
<br/>
]]
.row[.content[
<!-- ### &emsp; Besides all the markdown features that we [already saw](#markdown): -->
## .color-main3[Add citations] along the text using the .amber[@ tags] from the .bib file:
]]
]
.row.split-two[
.column.slide-in-left.bg-purple[.content.v30[
### This

```{}
Characteristics of Open Science, following @Fecher2014:

"Our professional network is valuable. It is also limited.
Perhaps there are people who are well-placed to help us,
in another university or company, in a different country,
but we unfortunately do not know them. Surely science
would proceed faster if we could reach those people?
Or, better, if they could find us?"[@woelfle2011open;
@Fecher2014]
```
]]
.column.slide-in-right[.content.v40[
### Becomes this
.font0-85[Characteristics of Open Science, following .color-main3[Fecher and Friesike (2014)]:
<br/>
“Our professional network is valuable. It is also limited.   
Perhaps there are people who are well-placed to
help us,   
in another university or company, in a different country,   
but we unfortunately do not know them.
Surely science   
would proceed faster if we could reach those people?   
Or, better, if they could find us?” .color-main3[(Woelfle,
Olliaro, and Todd 2011; Fecher and Friesike 2014)].]
]]
]
---
class: split-30

.row.split-two[
.row[.content[
#  Edit the text and code section
<br/>
]]
.row[.content[
## .blue[Add a list of references] at the end of the document by typing .amber[References]:
]]
]
.row.split-two[
.column.slide-in-left.bg-indigo[.content.v10[
### This

```{}
"Our professional network is valuable. It is also limited.
Perhaps there are people who are well-placed to help us,
in another university or company, in a different country,
but we unfortunately do not know them. Surely science
would proceed faster if we could reach those people?
Or, better, if they could find us?"[@woelfle2011open;
@Fecher2014]

References
```
]]
.column.slide-in-right[.content.v40.pad10px[
### Becomes this
.font0-85[
“Our professional network is valuable. It is also limited.   
Perhaps there are people who are well-placed to
help us,   
in another university or company, in a different country,   
but we unfortunately do not know them.
Surely science   
would proceed faster if we could reach those people?   
Or, better, if they could find us?” .purple[(Woelfle,
Olliaro, and Todd 2011; Fecher and Friesike 2014)].
.font_medium[References]  
Fecher, Benedikt, and Sascha Friesike. 2014. “Open Science: One Term, Five Schools of Thought.” In
Opening Science: The Evolving Guide on How the Internet Is Changing Research, Collaboration and Scholarly
Publishing, edited by Sönke Bartling and Sascha Friesike, 17–47. Cham: Springer International Publishing.
https://doi.org/10.1007/978-3-319-00026-8_2.  
Woelfle, Michael, Piero Olliaro, and Matthew H Todd. 2011. “Open Science Is a Research Accelerator.”
Nature Chemistry 3 (10): 745–48.
2
]

]]
]

---
class: split-30

.row.split-two[
.row[.content[
#  Edit the text and code section
<br/>
]]
.row[.content[
## .teal[Add R code] along the text using .amber[backticks] and .amber[curly braces]:
]]
]
.row.split-two[
.column.slide-in-left.bg-teal[.content.v30[
### This code chunk

````markdown
`r ''````{r eval = FALSE, echo = TRUE}
library(ape)
data(chiroptera)
str(chiroptera)
```
````


### And this inline code

You can know the number of tips in your Chiroptera tree with `length(chiroptera$tip.label)`.

]]
.column.slide-in-right[.content.v30[
### renders this

```{r eval = TRUE}

library(ape)
data(chiroptera)
str(chiroptera)
```

### will render this

My Chiroptera tree has `r length(chiroptera$tip.label)` tips.

]]
]
---
class: split-30

.row.split-two[
.row[.content[
# Edit the text and code section
<br/>
]]
.row[.content[
## .green[Embed the output of R code] along the text using .amber[backticks] and .amber[curly braces]:
]]
]
.row.split-two[
.column.slide-in-left.bg-light-green[.content.v30[
### This code chunk

````markdown
`r ''````{r eval = TRUE}
library(ape)
data(chiroptera)
str(chiroptera)
```
````
<!-- tip to embed code from here https://support.rstudio.com/hc/en-us/articles/360018181633-Including-verbatim-R-code-chunks-inside-R-Markdown
AND HERE FOR JENNY BRYAN's COMPENDIUM:
https://rmarkdown.rstudio.com/articles_verbatim.html
-->

### And this inline code

My Chiroptera tree has ```  `r ''``{r} length(chiroptera$tip.label)`  ``` tips.

]]
.column.slide-in-right[.content.v30[
### renders this

```{r eval = TRUE, echo = FALSE}
library(ape)
data(chiroptera)
str(chiroptera)
```

### will render this

My Chiroptera tree has `r length(chiroptera$tip.label)` tips.

]]
]

---
class: split-40

.row.split-30[
.row[.content[
# Edit the text and code section
<br/>
]]
.row[.content[
## .deep-orange[Add a plot] without showing the code by setting .amber[echo] to .amber[FALSE] <br/> Control its quality with the .amber[fig.retina] option and its size with .amber[fig.height] and .amber[fig.width]:
]]
]
.row.split-60[
.column.slide-in-left.bg-deep-orange[.content[
### This code chunk
<br/><br/><br/>
<pre><code>```{r eval = TRUE, echo = FALSE, fig.height = 5, fig.retina = 3}
plot(chiroptera, type = "c", cex = 0.3)
```</code></pre>
]]
.column.slide-in-right[.content[
### renders this

```{r eval = TRUE, echo = FALSE, fig.height = 5, fig.retina = 3}
plot(chiroptera, type = "c", cex = 0.3)
```


]]
]
---
class: split-30

.row.split-two[
.row[.content[
# Edit the text and code section
<br/>
]]
.row[.content[
## .deep-purple[Add a table] with some formatting with the function .amber[kable] from the .amber[knitr] package:
]]
]
.row.split-40[
.column.slide-in-left.bg-deep-purple[.content[
### This code chunk
<br/><br/>
<pre><code>```{r eval = TRUE, echo = FALSE}
knitr::kable(iris[1:5, ], caption = 'A caption')
```</code></pre>
]]
.column.slide-in-right[.content[
### Becomes this
<br/><br/>
```{r eval = TRUE, echo = FALSE}
knitr::kable(iris[1:5, ], caption = 'A caption')
```


]]
]
---
class: split-40

.row.split-two[
.row[.content[
# Edit the text and code section 
<br/>
]]
.row[.content[
## Control your .deep-orange[code variables] globally by setting options on the .amber[setup chunk], i.e., the first R code chunk on the .Rmd file:
]]
]
.row.split-60[
.column.slide-in-left.bg-deep-orange[.content.v40[
<pre><code>```{r setup}
knitr::opts_chunk$set(fig.retina = 3, warning = FALSE, message = FALSE)
```</code></pre>
]]
.column.slide-in-right[.content.v40.center[
### These can be individually overriden on each chunk, in case you want to show a code warning, for example.
]]
]
